Concurrent Programming with Harmony

### 2020-07-30 book/paper.tex
Updated barrier

Barrier synchronization is a problem that comes up in high-performance
parallel computing, used, among others, for scalable simulation.
A barrier is almost the opposite of a critical section:
the intention is to get a group of processes to run some code at the
same time, instead of having them execute it one at a time.
More precisely, with barrier synchronization the processes execute in rounds.
Between each round there is a so-called \emph{barrier} where processes wait
until all processes have completed the round and before they start the
next one.
For example, in an iterative matrix algorithm, the matrix may be
cut up into fragments.  During a round, the processes run concurrently
one for each fragment.  The next round is not allowed to start
until all processes have completed processing their fragment.

\autoref{fig:barrierdiagram} shows a high-level depiction with three
processes.  Initially all processes are in round~0.  Then each process
can start and finish the round.  However, none of the processes can
progress to the next round until all processes have finished the
current round.

>>>>

Barrier synchronization is a problem that comes up in high-performance
parallel computing, used, among others, for scalable simulation.
A barrier is almost the opposite of a critical section:
the intention is to get a group of processes to run some code at the
same time, instead of having them execute it one at a time.
More precisely, with barrier synchronization the processes execute in rounds.
Between each round there is a so-called \emph{barrier} where processes wait
until all processes have completed the previous round, before they start the
next one.
For example, in an iterative matrix algorithm, the matrix may be
cut up into fragments.  During a round, the processes run concurrently,
one for each fragment.  The next round is not allowed to start
until all processes have completed processing their fragment.

\autoref{fig:barrierdiagram} shows a high-level depiction of barrier synchronization
with three and processes.  Initially all processes are in round~0.  Then each process
can start and finish the round.  However, none of the processes can
progress to the next round until all processes have finished the
current round.
